### 2025-09-29 src/articles/article13.qmd

1. Evidence will be distributed by the Arbiter between twenty-four and forty-eight hours before the hearing date and time.
1. The dress at the hearing will be informal.
1. Witnesses may volunteer to speak on behalf or against the charges.
   a. The witnesses may volunteer by giving a written message to the Arbiter stating their intent to participate and stance at least three hours before the hearing.\
   a. Witnesses will be advised by the Arbiter that they are not to discuss the hearing or the accusation outside of the hearing.
   a. The Arbiter will call the hearing to order.

@@

1. The chapter may issue sanctions within its scope. The following are suggested examples of possible sanctions:\
   a. Counseling
   a. Loss of housing status
   a. Loss of voting privileges
   a. Recommendation of Removal from an Elected Position
   a. Recommendation of Suspension
   a. {{< var glossary.probation >}}

>>>>

1. Evidence will be distributed by the Arbiter between twenty-four and forty-eight hours before the hearing date and time.
1. The dress at the hearing will be informal.
1. Witnesses may volunteer to speak on behalf or against the charges.
   a. The witnesses may volunteer by giving a written message to the Arbiter stating their intent to participate and stance at least three hours before the hearing.
   a. Witnesses will be advised by the Arbiter that they are not to discuss the hearing or the accusation outside of the hearing.
   a. The Arbiter will call the hearing to order.

@@

1. The chapter may issue sanctions within its scope. The following are suggested examples of possible sanctions:
   a. Counseling
   a. Loss of housing status
   a. Loss of voting privileges
   a. Recommendation of Removal from an Elected Position
   a. Recommendation of Suspension
   a. {{< var glossary.probation >}}

### 2025-09-29 src/articles/article4.qmd

1. Officer Elections
   a. Officers will be elected by {{< var glossary.simple-majority >}} vote.
   a. In the case that no nominee receives a {{< var glossary.simple-majority >}}, there will immediately be another vote between all candidates who received the two highest counts of votes.\
   a. Nominations for president and treasurer must be a week before nominations for the other positions in order to make time for {{< var acronyms.cab >}} interviews.

>>>>

1. Officer Elections
   a. Officers will be elected by {{< var glossary.simple-majority >}} vote.
   a. In the case that no nominee receives a {{< var glossary.simple-majority >}}, there will immediately be another vote between all candidates who received the two highest counts of votes.
   a. Nominations for president and treasurer must be a week before nominations for the other positions in order to make time for {{< var acronyms.cab >}} interviews.
